Filtering in the flowCore package

### 2006-12-13 inst/doc/filtering-flowCore.Rnw
* Fixed (I think) bug in filtering-flowCore.Rnw that was causing it to fail R CMD build * Improved and fixed some aspects of multipleFilterResult to get more natural usage * Implemented 1-d k-means to split a well-defined mixture of populations into 2 or more named populations. I was thinking about FCB during implementation. * Improved implementation of "split" to handle multiple population case.
MILESTONE-- I can now complete all preprocessing for my use case except for transformation and some outlier removal associated with the transformation, which I had to do "by hand."  

git-svn-id: http

Implementing a new filter is a fairly straightforward process requiring the definition of a filtering class, derived from the \Rclass{filter} base class, and, at the minimum, the definition of an \Rfunction{%in%} method.

\subsection{Customzing a \Robject{filter} class}

>>>>

Implementing a new filter is a fairly straightforward process requiring the definition of a filtering class, derived from the \Rclass{filter} base class, and, at the minimum, the definition of an \Rfunction{\%in\%} method.

\subsection{Customizing a \Rclass{filter} class}
